Self Referencing Sequences

### 2014-11-07 draft.tex
fixed up intro again

Above was an example where the blocks always have elements be either $1$ or $2$. Since we are self-referincing with respect to block lengths, the particular value that the block takes is not as important as the block lengths. Whenever the sequence can only takes two possible numbers, the values of the blocks is unambiguous; the block values simply alternate. As in the sequence above, after a block of 1's, the next block must be a block of 2's and vice versa. However if our sequence was composed of $1$'s, $2'$s and $3'$s there would be ambiguity over which number a new block should begin with.

For example if the first number is 1, then we could make the second number either a 2, or a 3. In particular, both:
\begin{equation}
1, 3, 3, 3, 2, 2, 2, \dots
\end{equation}
\begin{equation}
1, 2, 2, 1, 1, 3, 1, \dots\\
\end{equation}
are in some sense self-referencing sequences.
Each time we need to specify a new block, we have a choice of two elements. We would like to avoid having a large number of choices in the generation of the sequence, and so we will use the convention that the order in which the elements are presented gives the order they are used in the sequence. 
For example, $(123 )$ will have a order $1 \rightarrow 2 \rightarrow 3 \rightarrow 1$.

@@

We call the set the sequence is generated over, along with its order the \emph{generating cycle}.

Our main results are:
\begin{itemize}
\item The self-referencing sequence for a given generating cycle is uniquely determined by its first number.
% This doesn't really mean anything... - erik
%
%\item Some characterizations of sequences with the same generating cycle.
\item For some generating cycles there exists an equivalent formulation of self-referencing sequences using substitution rules
\item If a generating cycle has substitution rules then one can compute the limiting density for the numbers in the sequence if a limiting density exists.
\item The limiting densities of the self-referencing sequences of  $(13)$ if such densities exists.
\end{itemize}

In Section~\ref{determinism} we show that if we are given a generating cycle and a starting number for the sequence, the sequence is uniquely determined. In Section~\ref{equivalence}, we consider the limiting behavior of such sequences, and we conjecture that the limiting behavior of a sequence is determined only by the generating cycle, and not the starting number.

In Section~\ref{iterativeprocess}, we show that there is an alternate way of generating them with an iterative process. In Section~\ref{substitutionrules}, we show how a large number of these sequences can actually be generated with a simple set of substitution rules. We introduce the density problem in Section~\ref{density}, and use ideas developed in Section~\ref{iterativeprocess} and Section~\ref{substitutionrules} to answer the question for certain types of generating cycles. Unfortunately, we find that the open problem of determining the density of the sequences generated by $(12)$ is hard to solve using our methods.

>>>>

Above was an example where each block contains either $1$'s or $2$'s. Whenever the sequence can only take two possible numbers, the number in the block is unambiguous; the numbers simply alternate. As in the sequence above, after a block of 1's, the next block must be a block of 2's, then again 1's, and vice versa. However if our sequence was composed of $1$'s, $2$'s and $3$'s there would be ambiguity over which number a new block should begin with.

For example if the first number is 1, then we could make the second number either a 2, or a 3. In particular, both:
\begin{equation}
1, 3, 3, 3, 2, 2, 2, \dots
\end{equation}
\begin{equation}
1, 2, 2, 1, 1, 3, 1, \dots\\
\end{equation}
are in some sense self-referencing sequences.
Each time we need to specify a new block, we have a choice of two elements. We would like to avoid having a large number of choices in the generation of the sequence, and so we will give the possible elements as a cycle. 
For example, self-referencing sequences with elements from the cycle $(123 )$ contain the elements 1, 2, and 3 and will have a order $1 \rightarrow 2 \rightarrow 3 \rightarrow 1$.

@@

We call the cycle the self-referencing sequence is generated over the \emph{generating cycle}.

Our main results are:
\begin{itemize}
\item The self-referencing sequence for a given generating cycle is uniquely determined by its first number.
\item Some properties in the limiting behavior of self-referencing sequences generated by the same cycle.
\item For some generating cycles there exists an equivalent formulation of self-referencing sequences using substitution rules.
\item If a generating cycle has substitution rules then one can compute the limiting density for the numbers in the sequence if such a limiting density exists.
\item The limiting densities of the self-referencing sequences of  $(13)$ if such densities exists.
\end{itemize}

In Section~\ref{determinism} we show that if we are given a generating cycle and a starting number for the sequence, the sequence is uniquely determined. In Section~\ref{equivalence}, we consider the limiting behavior of such sequences.

In Section~\ref{iterativeprocess}, we give a procedure generating self-referencing sequences with an iterative process. In Section~\ref{substitutionrules}, we show how a large number of these sequences can actually be generated with a simple set of substitution rules. We introduce the density problem in Section~\ref{density}, and use ideas developed in Section~\ref{iterativeprocess} and Section~\ref{substitutionrules} to answer the question for certain types of generating cycles. Unfortunately, we find that the open problem of determining the density of the sequences generated by $(12)$ is hard to solve using our methods.
